A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean

### 2021-01-20 03_Prep_data.Rmd
Remove code removing trials not reporting variance, already done;
correct KableExtra::add_footnote syntax

```{r variance_types}
PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   group_by(trial_ref, location, year , Y_error_type) %>%
   summarise(DMI_treatments = length(Y_error_type), .groups = 'drop') %>%
   arrange(Y_error_type) %>%
   kable(caption = "Number of treatments for each trial and the error type reported",
         align = "c") %>%
   footnote(general = "DMI - demethylation inhibitors (tebuconazole and propiconazole).")
```

@@

### Formatting Variance

First let's check for any entries missing variance and remove them.

```{r remove_studies}
any(is.na(PM_MB_dat$yield_error))

PM_MB_dat <-
   PM_MB_dat[!is.na(PM_MB_dat$yield_error), ]

PM_MB_dat$vi <- PM_MB_dat$yield_error
```

>>>>

```{r variance_types}
PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   group_by(trial_ref, location, year , Y_error_type) %>%
   summarise(DMI_treatments = length(Y_error_type), .groups = 'drop') %>%
   arrange(Y_error_type) %>%
   kable(caption = "Number of treatments for each trial and the error type reported",
         align = "c") %>%
   kableExtra::add_footnote(label = "DMI - demethylation inhibitors (tebuconazole and propiconazole).", notation = "none")
```

@@
